---
title: "Lab 10"
author: "Deanna Elliott"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(usethis)
library(beepr) 
library(praise)
library(cowsay) 
library(paletteer) 
library(sf) 
library(janitor)
```

## Cool & Sometimes Useful Stuff

### Use the function 'beep()' in the beepr package to make an audio alert when your code is done running.

#### Sounds 1 - 15

```{r, eval = FALSE}

# create sequence of 99 down to 1

for(i in rev(seq(1:99))) {
  
  print(paste(i, "bottles of beer on the wall"))

} 

# beep(4)
```


### praise and cowsay

Packages built with a single purpose: to be kind and fun

```{r}

praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!!")

praise("Holy ${creating}, Batman - this code is ${adjective}")
```
Use cowsay::say to make a character say something to you

```{r}

say("WOW!", by = "spider")
```

## Make .Rmd a git repo... usethis::use_git()

## usethis::use_github() to open and edit new repo

## Use paletteer to access thousands of color palettes

```{r}

storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure)
```

